---
title: "MATH 216 Data Science Final Project (Fall 2016)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
output: 
  html_document: 
    keep_md: yes
---


* Name: Alexander Pastora
* Project title: Predicting a Good Star Rating for Restaurant on Yelp
* Write-up on RPubs: <http://rpubs.com/pinkfan9999/Final_Project>
* Abstract: This study looked at star ratings of restaurants in Charlotte, Las Vegas, Madison, Phoenix, Pittsburgh and Urbana_Champaing. Specifically, this data was used to create a model that attempts determine if a Good Star Rating (greater than 3 out of 5) could be determined from certain attributes of a restaurant. In addition to these attributes, demographic and income data were incorporated into the model. Although a model was created for the restaurant data, the model was only accurate about 63% of the time. This suggests that predicting a restaurant's rating by attributes and location is not an accurate method. This may suggest that, for the restaurant data, other factors such as the quality and taste of the food may be more important.


```{r, echo=FALSE, message=FALSE}
#
# Include code for one plot here
#
library(ggplot2)
library(dplyr)
yelp_US_restaurants <- read_csv("yelp_US_restaurants.csv")
# Stars vs. Price Range 
ggplot(data=yelp_US_restaurants, aes(x=yelp_US_restaurants$'attributes.Price Range', y=stars, group=yelp_US_restaurants$'attributes.Price Range')) +geom_boxplot()
```
This graph is example of some of the Exploratory Analysis done in this paper. It is specifically looking at how the distribution of star ratings changes with price range (out of 4).
